---
title: "Height And Weight Dataset"
author: "Anant Sharma"
date: "12/17/2019"
output: html_document
---

## 1) Loading the data

  ```{r direc}
    setwd('C:/Users/Anant Sharma/Desktop/DATA SCIENCE/Practice/Hight weight dataset')
    data<-read.csv("weight-height.csv")
  ```
  
## 2) Exploratory Analysis

There is a linear relationship between height and weight which is shown by the following scatterplot. 

  ```{r plot1}
    library(ggplot2)
    g<-ggplot(data=data,aes(x=Weight,y=Height))
    g+geom_point()+geom_smooth(method='lm')
  ```
  
The following boxplots shows that male tend to have more height and weight than female.

  ```{r plot2}
    g<-ggplot(data=data,aes(x=Gender,y=Weight))
    g+geom_boxplot()
    
    f<-ggplot(data=data,aes(x=Gender,y=Height))
    f+geom_boxplot()
  ```  
  
## 3) Fitting the model

We would use linear regression for this data and we would be prediciting weight using height and gender.

  
## 3.1) Splitting the data

  ```{r split}
    library(caret)
    intrain<-createDataPartition(y=data$Weight,p=0.7,list=FALSE)
    train<-data[intrain,]
    test<-data[-intrain,]
  ```
  
## 3.2) Model fitting
  ```{r fit}
    fit<-lm(Weight~.,data=train)
    pre<-predict(fit,test)
    library(MLmetrics)
    MSE(pre,test$Weight)
  ```
We get an mse of 100 approx.


    
    
  
  
  
  